Refunctionalization of Abstract Abstract Machines (Functional Pearl)

### 2018-03-17 paper.tex
Proofreading intro to 7, my last commit for the night

As identified before, there are two layers of continuations, one for the normal stack of 
the analyzed language, and the other for the nondeterministic choices of closures.
This corresponds to the extended continuation-passing style.
But in our defining language Scala, the delimited controls rely on the continuation-passing
transformation which is only one layer.
To address this problem, base on the @nd@ operator we have before, we introduce 
another operator @ndcps@ for handling non-deterministic choices.

The @ndcps@ itself is implemented with delimited controls. 
The function takes two arguments: a set of elements with type @T@ and an initial 
accumulated value of type @Set[S]@. 
Function @ndcps@ iteratively returns a value of type @T@ with annotated by
@@cps[Set[T]]@ that denotes the final returned value of @ndcps@ is type @Set[T]@.
The @f@ introduced by the @shift@ operator is the delimited continuation at the 
call-site of @ndcps@.

@@

We add an annotation @@cps[Ans]@ on the return type of function @aeval@.
Now for every non-deterministic choices in the abstract interpreter

>>>>

As previously identified, there are two layers of continuations: one for the normal stack of the analyzed language, and the other for the nondeterministic choices of closures.
This corresponds to the extended continuation-passing style.
But in our defining language (Scala), the delimited controls rely on the continuation-passing transformation which is only one layer.
To address this problem, based on the @nd@ operator we have before, we introduce another operator @ndcps@ for handling non-deterministic choices.

The @ndcps@ itself is implemented with delimited controls.
The function takes two arguments: a set of elements with type @T@, and an initial accumulated value of type @Set[S]@.
The @ndcps@ function iteratively returns a value of type @T@ with annotated by
\texttt{\@ cps[Set[T]]} \note{JD: Tiark, can you fix the at sign? I fixed it for the other paper, but my fix doesn't work here} that denotes the final returned value of @ndcps@ is type @Set[T]@.
The @f@ introduced by the @shift@ operator is the delimited continuation at the call-site of @ndcps@.

@@

We add an annotation \texttt{ cps[Ans]} on the return type of the @aeval@ function.
Now, for every nondeterministic choice in the abstract interpreter, we can simply call @ndcps@ on them and write the program sequentially as a concrete interpreter.
The cache is still accumulated by the next call to @ndcps@ or @aeval@, given the fact that the abstract interpreter should always use the latest cache.
